\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    {\fontsize{14}{16}\selectfont \textbf{VIETNAM NATIONAL UNIVERSITY, HANOI}\par}
    {\fontsize{14}{16}\selectfont \textbf{VIETNAM JAPAN UNIVERSITY}\par}
    \vspace{2cm}
    
    {\fontsize{14}{16}\selectfont \textbf{BACHELOR PROGRAM}\par}
    {\fontsize{14}{16}\selectfont \textbf{COMPUTER SCIENCE AND ENGINEERING}\par}
    
    \vspace{3cm}
    
    {\fontsize{20}{24}\selectfont \textbf{INTERNSHIP REPORT}\par}
    \vspace{1cm}
    {\fontsize{18}{21}\selectfont \textbf{DEVELOPMENT OF A COMPREHENSIVE}\par}
    {\fontsize{18}{21}\selectfont \textbf{REAL-TIME INFANT MONITORING SYSTEM}\par}
    
    \vspace{4cm}
    
    \begin{flushleft}
    \hspace{2.5cm} \textbf{Internship Unit:} NTQ Solutions JSC (NTEX) \\
    \vspace{0.5cm}
    \hspace{2.5cm} \textbf{Supervisor:} Mr. Le Van Luc \\
    \vspace{0.5cm}
    \hspace{2.5cm} \textbf{Student Name:} Nguyen The Nam \\
    \vspace{0.5cm}
    \hspace{2.5cm} \textbf{Student ID:} 22110158
    \end{flushleft}
    
    \vfill
    
    {\fontsize{14}{16}\selectfont \textbf{Hanoi, 2025}\par}
\end{titlepage}

% =================================================================================
%                                   ACKNOWLEDGEMENTS
% =================================================================================
\newpage
\pagenumbering{roman} 
\phantomsection
\addcontentsline{toc}{section}{Acknowledgements}
\section*{ACKNOWLEDGEMENTS}

I would like to express my sincere gratitude to the Board of Directors and the staff of NTQ Solutions Joint Stock Company, particularly the NTEX Division, for providing a professional and stimulating working environment. The modern facilities and supportive culture significantly contributed to the success of this internship.

I am deeply indebted to my direct supervisor, Mr. Le Van Luc. His expert guidance on embedded systems, cloud architecture, and AI deployment was instrumental in my professional development. His mentorship extended beyond technical skills, offering valuable insights into project management and problem-solving strategies that were crucial for the completion of the "Baby Cry Monitor v2.2" project.

I also wish to thank the faculty members of the School of Computer Science and Engineering at Vietnam Japan University (VNU). The rigorous academic foundation in algorithms, software engineering, and artificial intelligence provided by the university was essential for addressing the complex challenges encountered during this project.

Finally, I am grateful to my family and friends for their unwavering encouragement and support throughout my academic journey.

Despite my best efforts, this report may contain limitations due to time constraints and experience. I welcome any constructive feedback from lecturers and industry professionals to further refine my skills.

\vspace{1cm}
\begin{flushright}
    \textit{Hanoi, December 30, 2024} \\
    \textbf{Student} \\
    \vspace{2cm}
    \textbf{Nguyen The Nam}
\end{flushright}

% =================================================================================
%                            LIST OF ABBREVIATIONS
% =================================================================================
\newpage
\phantomsection
\addcontentsline{toc}{section}{List of Abbreviations}
\section*{LIST OF ABBREVIATIONS}

\begin{center}
\begin{longtable}{|l|p{10cm}|}
\hline
\textbf{Abbreviation} & \textbf{Definition} \\
\hline
AI & Artificial Intelligence \\
\hline
API & Application Programming Interface \\
\hline
CNN & Convolutional Neural Network \\
\hline
IoT & Internet of Things \\
\hline
JWT & JSON Web Token \\
\hline
MQTT & Message Queuing Telemetry Transport \\
\hline
REST & Representational State Transfer \\
\hline
STFT & Short-Time Fourier Transform \\
\hline
YOLO & You Only Look Once \\
\hline
R\&D & Research and Development \\
\hline
UI/UX & User Interface / User Experience \\
\hline
\end{longtable}
\end{center}
