\newpage
\pagenumbering{arabic} 
\setcounter{page}{1}

\section{OVERVIEW OF THE INTERNSHIP UNIT}

\subsection{Introduction to NTQ Solutions}
Established in 2011, NTQ Solutions Joint Stock Company (NTQ) has emerged as a premier technology provider in Vietnam, delivering software solutions and IT services to a global clientele. Headquartered in Hanoi, with strategic branches in Japan, South Korea, and Hong Kong, NTQ has solidified its standing in the international technology market.

The company's mission is to provide "World-class" technology solutions that address complex business challenges while fostering a positive and productive work environment for its employees.

Within the organizational structure, NTEX (NTQ Technology Extension) operates as a specialized strategic unit focused on the Research and Development (R\&D) of emerging core technologies. NTEX serves as an incubator for innovation, prioritizing advancements in the Internet of Things (IoT), Artificial Intelligence (AI), Robotics, and Blockchain to create high-tech "Make in Vietnam" products.

\subsection{Organizational Structure and Work Environment}
NTQ Solutions adopts a flat organizational model designed to facilitate open communication and collaboration across all levels. My internship was conducted within the R\&D Department of the NTEX division.

The R\&D team comprises experienced specialists in embedded systems and artificial intelligence. The work environment is characterized by its dynamism and professionalism, strictly adhering to international software development standards such as Agile/Scrum and CMMi. Knowledge sharing is a core value, exemplified by weekly "Tech Talk" sessions where team members exchange insights on recent technological advancements.

\subsection{Key Activities of the R\&D Department}
The R\&D department concentrates its efforts on three primary domains:
\begin{itemize}
    \item \textbf{Edge AI Optimization:} Developing and optimizing deep learning models for deployment on resource-constrained hardware, including Raspberry Pi, NVIDIA Jetson, and ESP32 microcontrollers.
    \item \textbf{Smart Ecosystems:} Designing intelligent solutions for healthcare and daily living, such as Elderly Monitoring Systems, Baby Monitors, and Smart Home Hubs.
    \item \textbf{Computer Vision Applications:} Implementing advanced computer vision techniques for facial recognition, behavioral analysis, and automated industrial inspection.
\end{itemize}
